---
title: "final_project"
author: "Kee-Young Shin"
date: "December 5, 2018"
output: html_document
---

```{r}
library(tidyverse)
library(readxl)
library(plotly)
```

## import hate crime incident count from 2005 to 2017
```{r}
hate_offenses_2017 = read_xls("./data/table-1.xls") %>% 
  janitor::clean_names() %>% 
  filter(table_1 == "Total") %>% 
  mutate(table_1 = str_replace(table_1, "Total", "2017"))

hate_offenses_2016 = read_xls("./data/2016_hatecrime.xls") %>% 
  janitor::clean_names() %>% 
  filter(table_1 == "Total") %>% 
  mutate(table_1 = str_replace(table_1, "Total", "2016")) %>% 
  select(1:5)

hate_offenses_2015 = read_xls("./data/2015_hatecrime.xls") %>% 
  janitor::clean_names() %>% 
  filter(table_1 == "Total") %>% 
  mutate(table_1 = str_replace(table_1, "Total", "2015"))
    
hate_offenses_2014 = read_xls("./data/2014_hatecrime.xls") %>% 
  janitor::clean_names() %>% 
  filter(table_1 == "Total") %>% 
  mutate(table_1 = str_replace(table_1, "Total", "2014")) %>% 
  select(1:5)

hate_offenses_2013 = read_xls("./data/2013_hatecrime.xls") %>% 
  janitor::clean_names() %>% 
  filter(table_1 == "Total") %>% 
  mutate(table_1 = str_replace(table_1, "Total", "2013")) %>% 
  select(1:5)

hate_offenses_2012 = read_xls("./data/2011_hatecrime.xls") %>% 
  janitor::clean_names() %>% 
  filter(table_1 == "Total") %>% 
  mutate(table_1 = str_replace(table_1, "Total", "2012"))

hate_offenses_2011 = read_xls("./data/2011_hatecrime.xls") %>% 
  janitor::clean_names() %>% 
  filter(table_1 == "Total") %>% 
  mutate(table_1 = str_replace(table_1, "Total", "2011"))

hate_offenses_2010 = read_xls("./data/2010_hatecrime.xls") %>% 
  janitor::clean_names() %>% 
  filter(table_1 == "Total") %>% 
  mutate(table_1 = str_replace(table_1, "Total", "2010"))

hate_offenses_2009 = read_xls("./data/2009_hatecrime.xls") %>% 
  janitor::clean_names() %>% 
  filter(table_1 == "Total") %>% 
  mutate(table_1 = str_replace(table_1, "Total", "2009"))

hate_offenses_2008 = read_xls("./data/2008_hatecrime.xls") %>% 
  janitor::clean_names() %>% 
  filter(table_1 == "Total") %>% 
  mutate(table_1 = str_replace(table_1, "Total", "2008"))

hate_offenses_2007 = read_xls("./data/2007_hatecrime.xls") %>% 
  janitor::clean_names() %>% 
  filter(table_1 == "Total") %>% 
  mutate(table_1 = str_replace(table_1, "Total", "2007"))

hate_offenses_2006 = read_xls("./data/2006_hatecrime.xls") %>% 
  janitor::clean_names() %>% 
  filter(table_1 == "Total") %>% 
  mutate(table_1 = str_replace(table_1, "Total", "2006"))

hate_offenses_2005 = read_xls("./data/2005_hatecrime.xls") %>% 
  janitor::clean_names() %>% 
  filter(table_1 == "Total") %>% 
  mutate(table_1 = str_replace(table_1, "Total", "2005"))

# aggregate data for all years
hatecrime_count_df = rbind(hate_offenses_2017, hate_offenses_2016, hate_offenses_2015, 
                           hate_offenses_2014, hate_offenses_2013, hate_offenses_2012,
                           hate_offenses_2011, hate_offenses_2010, hate_offenses_2009,
                           hate_offenses_2008, hate_offenses_2007, hate_offenses_2006,
                           hate_offenses_2005) %>% 
  select(1:3) 
  
colnames(hatecrime_count_df) = c("year", "total_incidents", "total_offenses")
```

## plot change in number of hate crimes over time
```{r}
hatecrime_count_df %>% 
  ggplot(aes(x = year, y = total_incidents)) + geom_line(group = 1, color = "blue")
```

## importing hate crime and predictors dataset
```{r}
# data in 2016
income = read_csv("./data/Income.csv") %>% 
  janitor::clean_names()

unemployment = read_csv("./data/Unemployment.csv") %>% 
  janitor::clean_names()

education = read_csv("./data/Educational_level.csv") %>% 
  janitor::clean_names()

ctizenship = read_csv("./data/Ctizenship.csv") %>% 
  janitor::clean_names()

race = read_csv("./data/Race.csv") %>% 
  janitor::clean_names()

vote = read_csv("./data/Vote.csv") %>% 
  janitor::clean_names()

crime_rate = read_excel("./data/2016.xls",  range = cell_rows(3:54)) %>%
  janitor::clean_names() %>%
  filter(participating_state != "Total") %>%
  select(location = participating_state, population_covered,       total_number_of_incidents_reported) %>%
  mutate(crime_rate = total_number_of_incidents_reported/population_covered*100000)

crime_rate_10_days = read_csv("./data/hate_crime_10days.csv") %>%
  janitor::clean_names()%>%
  select(location = state, hate_crime_10_day = hate_crimes_per_100k_splc)

ctizenship =
  ctizenship %>% 
  select(location, non_citizen)

race =
  race %>% 
  select(location, white)

crime_rate =
  crime_rate %>% 
  select(location, crime_rate)

merge_data = 
  merge(income, unemployment, by = "location") %>% 
  merge(., education, by = "location") %>% 
  merge(., ctizenship, by = "location") %>% 
  merge(., race, by = "location") %>% 
  merge(., vote, by = "location") %>%
  merge(., crime_rate, by = "location") %>%
  merge(., crime_rate_10_days, by = "location") %>%
  filter(location != "United States") %>% 
  rename(state = location, share_unemployed = unemployed, share_non_citizen = non_citizen, share_white = white)
```


#dataset for annual report in state division
```{r}
#list
df = list.files(path = "./annual")
#function
read_data = function(x){read_excel(str_c("./annual/", x),  range = "A3:E54")%>%
    mutate(year = x)}
#map
hate_crime = map(df, read_data)%>%
  bind_rows()%>%
  janitor::clean_names()%>%
  select(-agencies_submitting_incident_reports, -agencies_submitting_incident_reports_2,-agencies_submitting_incident_reports_3)%>%
  mutate(year = str_replace(year, ".xls", ""))%>%
  select(year, everything())
#set na to 0
hate_crime[is.na(hate_crime)]=0

#complete the final dataset
hate_crime = hate_crime%>%
  mutate(total_incident = total_number_of_incidents_reported + total_number_of_incidents_reported_2)%>%
  select(year, state = participating_state, population = population_covered, total_incident)%>%
  filter(state != "Total") %>%
  mutate(annualprop = total_incident/population*100000)%>%
  mutate(year = str_replace(year, ".xls", ""))%>%
  filter(state!="Guam1")
```



do the further cleaning of the merge data

```{r}
merge_data = merge_data %>%
  mutate(median_annual_household_income = str_replace(median_annual_household_income, ",", "")) %>%
  mutate(median_annual_household_income = gsub("\\$", "",median_annual_household_income )) %>%
mutate(median_annual_household_income = as.numeric(median_annual_household_income)) %>%
  select(state, median_income = median_annual_household_income, everything())
```


## regression part
```{r}
sum(is.na(merge_data))
mle = lm(crime_rate~median_income+share_unemployed+share_population_with_high_school_degree+share_non_citizen+ share_white+ crime_rate, data = merge_data)
summary(mle)
multi.fit = step(mle, direction = 'backward')
summary(multi.fit)

# see distribution of crime rate 
merge_data %>% 
  ggplot(aes(x = crime_rate)) + geom_histogram()

# transform crime rate variable
merge_data_log = merge_data %>% 
  mutate(crime_rate = log(crime_rate)) 

mle_log = lm(crime_rate~median_income+share_unemployed+share_population_with_high_school_degree+share_non_citizen+ share_white, data = merge_data_log)

summary(step(mle_log, direction = "both"))

```

## see correlation between variables 
```{r}
merge_data %>%
  select(-state, -share_voters_voted_trump) %>%
  select(crime_rate, everything()) %>%
  pairs()
```

## see distribution of hate crime rate 
```{r}
ggplot(merge_data, aes(x = crime_rate)) + 
  geom_density(alpha = .4, adjust = .5, color = "blue")
```

##see whether Trump rate influence the model
```{r}
merge_data_log = merge_data_log%>%
  mutate(share_voters_voted_trump = sub("\\%", "",share_voters_voted_trump))%>%
  mutate(share_voters_voted_trump = as.numeric(share_voters_voted_trump)/100)

mle_log_1 = lm(crime_rate~median_income+share_unemployed+share_population_with_high_school_degree+share_non_citizen+ share_white+ share_voters_voted_trump, data = merge_data_log)
  
summary(step(mle_log_1, direction = "both"))

##see the correlation between trump and income
cor(merge_data_log$share_voters_voted_trump, merge_data_log$median_income)

```

###the final model 1 crime&income
```{r}
crime_income_slr =lm(crime_rate~median_income, data = merge_data_log)
summary(crime_income_slr)%>%
  broom::tidy()%>%
  knitr::kable()
```

###the final model 2 crime~Trump&income
```{r}
crime_trump_slr = lm(crime_rate~share_voters_voted_trump, data = merge_data_log)
summary(crime_trump_slr)%>%
  broom::tidy()%>%
  knitr::kable()
```

###the final model 3 crime&Trump&income
```{r}
mlr_trump_income = lm(crime_rate~share_voters_voted_trump + median_income, data = merge_data_log)
summary(mlr_trump_income)%>%
  broom::tidy()%>%
  knitr::kable()
```

## do scatter plot 
```{r}
merge_data_log%>%
  ggplot(aes(x = median_income,y = crime_rate))+
  geom_smooth(method = "lm", color="black", formula = y ~ x) +
  geom_point()

merge_data_log%>%
  ggplot(aes(x = share_voters_voted_trump, y = crime_rate))+
  geom_smooth(method = "lm", color="black", formula = y ~ x) +
  geom_point()
```


##Building the Map of hate crime rate based on 2016 
```{r}
map_data_2016 = merge_data %>%
  rbind(c("Hawaii",71223,	0.034, 0.904,	0 ,0.81, '33.1%', 0 ,0)) %>% 
  as.tibble() %>% 
  arrange(state)

map_data<-map_data_2016 %>%         
  mutate(
         state = as.factor(state),
         code = state.abb[state],
         code = c(code[1:8],'DC',code[9:50]),
         hover = with(map_data_2016, paste(state,'<br>' ,"share for trump",share_voters_voted_trump)),
         crime_rate = as.numeric(crime_rate)
         ) %>% 
  select(code, crime_rate, hover)

l <- list(color = toRGB("grey"), width = 1)
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = F
)


plot_geo(map_data, locationmode = 'USA-states') %>%
  add_trace(
    z = ~ crime_rate, text = ~hover, locations = ~code,
    color = ~ crime_rate, colors = 'Reds',marker = list(line = l)
  ) %>%
  colorbar(title = "Hate crime rate ") %>%
  layout(
    title = 'Hate crime rate in 2016 all over U.S. ',
    geo = g
  )
```


```{r}

library(reshape2)

hate_crime_10days<-read_csv("./data/hate_crime_10days.csv")
hate_crime_ave<-hate_crime %>% 
  na.omit() %>% 
  filter(year==2016) 


compare_rate<-merge(hate_crime_10days, hate_crime_ave, by= "state")

compare_rate %>% 
  mutate(hate_crimes_per_100k_after = hate_crimes_per_100k_splc/10 * 365) %>% 
  select(state, hate_crimes_per_100k_after, annualprop) %>% 
  melt(, id = "state") %>% 
  ggplot(aes(x = state, y = value, color = variable, group = variable))+
  geom_point()+
  geom_line()+
  theme(axis.text.x = element_text(angle = 90, hjust = 0.2))

 
  saveRDS(compare_rate,file = "./data/compare_data")
  
compare_rate %>% 
  mutate(hate_crimes_10days_year = hate_crimes_per_100k_splc/10 * 365) %>% 
  select(state, hate_crimes_10days_year, annualprop) %>% 
  melt(, id = "state") %>% 
  mutate(state = reorder(state, value)) %>% 
  ggplot(aes(x = state, y = value, fill = variable, group = variable)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, size = 10, hjust = 1),legend.position = "right")
```


change the bar plot

```{r}
compare_rate %>% 
  mutate(hate_crimes_10days_year = hate_crimes_per_100k_splc/10 * 365) %>% 
  select(state, hate_crimes_10days_year, annualprop) %>% 
  melt(, id = "state") %>% 
  mutate(state = factor(state, levels = state %>% unique %>% sort(decreasing = T))) %>% 
  ggplot(aes(x = state, y = value, fill = variable, group = variable))+
  geom_bar(stat="identity", position = "dodge", width = 0.5)+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 60))+
  coord_flip()
```


