---
title: "Shiny Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---
```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(viridis)
## Loading required package: viridisLite
library(p8105.datasets)
library(plotly)
library(readxl)
library(shiny)
```

```{r}

hate_crime<-read_csv("./data/hate_crime.csv")

l <- list(color = toRGB("white"), width = 2)

g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa')
)
```


Column {.sidebar}
-----------------------------------------------------------------------
```{r}
years = hate_crime %>% distinct(year) %>% pull()
selectInput("year_choice", label = h3("Select year"),
            choices = years, selected = "2010")
```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A
##prepare:
```{r}
```{r}
# data in 2016
income = read_csv("./data/Income.csv") %>% 
  janitor::clean_names()

unemployment = read_csv("./data/Unemployment.csv") %>% 
  janitor::clean_names()

education = read_csv("./data/Educational_level.csv") %>% 
  janitor::clean_names()

ctizenship = read_csv("./data/Ctizenship.csv") %>% 
  janitor::clean_names()

race = read_csv("./data/Race.csv") %>% 
  janitor::clean_names()

vote = read_csv("./data/Vote.csv") %>% 
  janitor::clean_names()

crime_rate = read_excel("./data/2016.xls",  range = cell_rows(3:53)) %>%
  janitor::clean_names() %>%
  filter(participating_state != "Total") %>%
  select(location = participating_state, population_covered,       total_number_of_incidents_reported) %>%
  mutate(crime_rate = total_number_of_incidents_reported/population_covered*100000) 


ctizenship =
  ctizenship %>% 
  select(location, non_citizen)

race = 
  race %>% 
  select(location, white)

crime_rate =
  crime_rate %>% 
  select(location, crime_rate)

merge_data = 
  merge(income, unemployment, by = "location") %>% 
  merge(., education, by = "location") %>% 
  merge(., ctizenship, by = "location") %>% 
  merge(., race, by = "location") %>% 
  merge(., vote, by = "location") %>%
  merge(., crime_rate, by = "location") %>% 
  filter(location != "United States") %>% 
  rename(state = location, share_unemployed = unemployed, share_non_citizen = non_citizen, share_white = white)%>%
  mutate(median_annual_household_income = str_replace(median_annual_household_income, ",", "")) %>%
  mutate(median_annual_household_income = gsub("\\$", "",median_annual_household_income )) %>%
mutate(median_annual_household_income = as.numeric(median_annual_household_income)) %>%
  select(state, median_income = median_annual_household_income, everything())
```
###end


```{r}
renderPlotly({  
  hate_crime %>% 
  mutate(
         state = as.factor(state),
         code = state.abb[state]
         ) %>% 
  select(year,code, everything()) %>% 
  filter(year == input$year_choice) %>% 
  plot_geo(locationmode = 'USA-states') %>%
  add_trace(
    z = ~ annualprop,  locations = ~code,
    color = ~ annualprop, colors = 'Greens'
  ) %>%
  colorbar(title = "Hate crime rate ") %>%
  layout(
    title = 'Hate crime rate in 2016 all over U.S. ',
        geo = g
  )
})
```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}
map_data_2016 = merge_data %>% 
  mutate(#hate_crimes_per_100k_splc = as.numeric(hate_crimes_per_100k_splc),
         #median_household_income = as.numeric(median_household_income),
         state = as.factor(state),
         code = state.abb[state],
         hover = with(merge_data, paste(state,'<br>' ,"share for trump",share_voters_voted_trump))
         ) %>% 
  select(code, crime_rate, hover )

l <- list(color = toRGB("white"), width = 2)
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)


plot_geo(map_data_2016, locationmode = 'USA-states') %>%
  add_trace(
    z = ~ crime_rate, text = ~hover, locations = ~code,
    color = ~ crime_rate, colors = 'Reds'
  ) %>%
  colorbar(title = "Hate crime rate ") %>%
  layout(
    title = 'Hate crime rate in 2016 all over U.S. ',
    geo = g
  )
```

### Chart C

```{r}

```