---
title: "Regression Analysis"
output: 
  html_document:
    toc: true
    toc_float:
      collapse: true
      smooth_scroll: false
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(plotly)
```

```{r, include = FALSE}
# data in 2016
income = read_csv("./data/Income.csv") %>% 
  janitor::clean_names()

unemployment = read_csv("./data/Unemployment.csv") %>% 
  janitor::clean_names()

education = read_csv("./data/Educational_level.csv") %>% 
  janitor::clean_names()

ctizenship = read_csv("./data/Ctizenship.csv") %>% 
  janitor::clean_names()

race = read_csv("./data/Race.csv") %>% 
  janitor::clean_names()

vote = read_csv("./data/Vote.csv") %>% 
  janitor::clean_names()

crime_rate = read_excel("./data/2016.xls",  range = cell_rows(3:53)) %>%
  janitor::clean_names() %>%
  filter(participating_state != "Total") %>%
  select(location = participating_state, population_covered,       total_number_of_incidents_reported) %>%
  mutate(crime_rate = total_number_of_incidents_reported/population_covered*100000) 


ctizenship =
  ctizenship %>% 
  select(location, non_citizen)

race = 
  race %>% 
  select(location, white)

crime_rate =
  crime_rate %>% 
  select(location, crime_rate)

merge_data = 
  merge(income, unemployment, by = "location") %>% 
  merge(., education, by = "location") %>% 
  merge(., ctizenship, by = "location") %>% 
  merge(., race, by = "location") %>% 
  merge(., vote, by = "location") %>%
  merge(., crime_rate, by = "location") %>% 
  filter(location != "United States") %>% 
  rename(state = location, share_unemployed = unemployed, share_non_citizen = non_citizen, share_white = white) %>% 
  mutate(median_annual_household_income = str_replace(median_annual_household_income, ",", "")) %>%
  mutate(median_annual_household_income = gsub("\\$", "",median_annual_household_income )) %>%
  mutate(median_annual_household_income = as.numeric(median_annual_household_income)) %>%
  select(state, median_income = median_annual_household_income, everything())
```

## Introduction

Since we found there was a significant increase in hate crime rate in 2016, we attempted to see which factors contributed to this change. To do this, we conducted regression analyses to determine the predictors that affected hate crime rate. These predictors included median annual household income, share of the population that is unemployed, share of the population with high school degree, share of the population that are not U.S. citizens, share of the population that is white, and the share of 2016 U.S. voters who voted for Donald Trump.

## Regression

###Model 1

We saw that the distribution for hate crime rate was quite skewed, so we first log transformed this value to acquire a more normal distribution. Then we performed regression on several common socioeconomic factors: median annual household income, share of the population that is unemployed, share of the population with high school degree, share of the population that are not U.S. citizens, share of the population that is white. Stepwise regression was used to create the best model, which yielded a simple linear regression model containing only one predictor: median household income. 


```{r, echo = FALSE}
merge_data_log = merge_data %>% 
  mutate(crime_rate = log(crime_rate)) %>%
  mutate(share_voters_voted_trump = sub("\\%", "",share_voters_voted_trump))%>%
  mutate(share_voters_voted_trump = as.numeric(share_voters_voted_trump)/100)
```

```{r, echo = FALSE}
crime_income_slr = lm(crime_rate~median_income, data = merge_data_log)
summary(crime_income_slr) %>%
  broom::tidy() %>%
  knitr::kable()

scatter_plot_1 = merge_data_log %>%
  ggplot(aes(x = median_income,y = crime_rate)) +
  geom_smooth(method = "lm", color = "blue", formula = y ~ x) +
  geom_point()+
  labs(
    title = "Scatterplot between hate crime rate and Median annual household income",
    x = "Median annual household income",
    y = "Log transformation of hate crime rate(per 100,000 population)",
    caption = "Data from FBI"
  )
ggplotly(scatter_plot_1)
```

$$log\textrm{ crime_rate} = -0.74 + 0.000021 \textrm{median_income}$$

As can be seen from the t-statistic and the p-value, median household income was not as significant of a factor. Additionally, we observed an association that was different than we had expected; there was a positive association meaning a higher median household income led to higher hate crime rates. However, we would be cautious in accepting these results judging by the lack of linear relationship shown by the scatter plot. 

###Model 2

We then included the share of U.S. citizens who voted for Donald Trump in 2016 to see if this would create a better model. As before, we performed log transformations on the outcome and used stepwise elimination on all previously entered predictors and the share of Trump voters. The results are shown below.  

```{r, echo = FALSE}
crime_trump_slr = lm(crime_rate~share_voters_voted_trump, data = merge_data_log)
summary(crime_trump_slr) %>%
  broom::tidy() %>%
  knitr::kable()

scatter_plot_2 = merge_data_log %>%
  ggplot(aes(x = share_voters_voted_trump, y = crime_rate)) +
  geom_smooth(method = "lm", color = "blue", formula = y ~ x) +
  geom_point()+
  labs(
    title = "Scatterplot between hate crime rate and shared voters who voted Trump",
    x = "shared voters voted Trump",
    y = "Log transformation of Hate crime rate(per 100,000 population)",
    caption = "Data from FBI"
  ) 
  ggplotly(scatter_plot_2)
```

$$log\textrm{ crime_rate} = 2.03 - 3.06 \textrm{share_voters_voted_trump}$$

Interestingly, including the proportion of Trump voters as a predictor resulted in median household income dropping from the model, while percent of Trump voters became a highly significant factor. The results showed a negative association between the predictor and the outcome; the higher the percent of Trump voters, the lower the rate of hate crime. Though the p-value was very small, the scatter plot again did not show an explicit linear relationship, therefore we will view these results with skepticism. These less than perfect regression results could be attributed to several factors such as confouders, multicollinearity amongst the socioeconomic predictors, and the small sample size. 
